\addcontentsline{toc}{chapter}{Resumen}

%-------------------------
%-------------------------
%-------------------------

\chapter*{Resumen}

%-------------------------
%-------------------------
%-------------------------

Este trabajo pretende obtener un algoritmo de computadora capaz de identificar estructuras CME analizando de manera indirecta su Tiempo de duración, Velocidad de la eyecta y Forma de la misma. Para ello será necesario usar Imágenes de SECCHI


%-------------------------
%-------------------------
%-------------------------

\cleardoublepage


\chapter*{Abstract}

%-------------------------
%-------------------------
%-------------------------

When the struts of the Apollo 11 Lunar Module met the powdery surface of the Moon on July 20, 1969, Commander Neil Armstrong marked the arrival with an eight-word message back home. 

''Houston,'' Armstrong said. ''Tranquility base here. The Eagle has landed.'' 

The time was 3:17 p.m. at mission control – four days, six hours and forty-six minutes after liftoff and more than eight years after President John F. Kennedy first challenged America to aim for the moon. The Apollo 11 crew had traveled 240,000 miles from Earth aboard the most complex machine ever conceived – guided by the most sophisticated computers ever built and boosted by the most powerful rocket ever launched – only to come within 30 seconds of running out of fuel. 

''Roger, Tranquility. We copy you down,'' came the reply from Charlie Duke in mission control. ''You got a bunch of guys down here about to turn blue.''


%-------------------------
%-------------------------
%-------------------------

\cleardoublepage

